Data

### 2019-02-18 analysis/data.Rmd
fixed few typos and markdown

PRU's [Open Reference Trajectory dataset](https://github.com/euctrl-pru/reftrj)
makes available the files needed for the analysis in this project,
you can retrieve them either by saving from your browser the relevant linked
flight and position files or use Google `gsutil` as follows:

@@

As explained in the paper, you can use `R/extract-arrivals.R` to get to CSV files
containing only the flights and positions for your airport of initerest.
You can edit the relevant configuration values at the beginning of the script before launching it.
Yuo will get:

* Flights details for arrivals at `<airport>` on `<date>`
  are in a CSV file `<airport>_flt_rt_<date>.csv`.
  For example `egll_flt_rt_2017-08-01.csv` is for arrivals to
  London Heathrow Airport (ICAO's id EGLL) on Aug, 1 2017.
  Key data items:
    * flight_id     unique flight identification
    * callsign      callsign flight identification of flight
    * aircraft_reg  aircraft registration
    * aircraft_type aircraft type, ICAO coding (e.g. A388, B772)
    * adep / ades   aerodrome of departure / destination

@@

The position reports within 40 nautical miles for arrival at
`<airport>` on `<date>`  are in a CSV file 
`<airport>_pos_rt_40NM_<date>.csv`.
These are a subset from `<airport>_pos_rt_<date>.csv`.
For example `eidw_pos_rt_40NM_2017-08-02.csv` is for arrivals'
positions within 40 nautical miles to Dublin Airport
(ICAO's id EIDW) on Aug, 2 2017.
Key data items:
  * flight_id     unique flight identification
  * timestamp     position report time
  * latitude      latitude coordinate (decimal notation)
  * longitude     longitude coordinate (decimal notation)
  * on_ground     on-ground / aloft flag
  * distance      [not sure ~~] miles flown [?]
  * distance_arp  distance position to aerodrome reference point

@@

>>>>

PRU's [Open Reference Trajectory dataset](https://github.com/euctrl-pru/reftrj)
makes available the files needed for the analysis in this project;
you can retrieve them either by saving the relevant linked
flight and position files from your browser or by using Google `gsutil` as follows:

@@

As explained in the paper, you can use `R/extract-arrivals.R` to produce CSV files
containing only the flights and positions for your airport of initerest.
You should edit the relevant configuration values at the beginning of the script before launching it.
You will get:

* Flights details for arrivals at `<airport>` on `<date>`
  are in a CSV file `<airport>_flt_rt_<date>.csv`.
  For example `egll_flt_rt_2017-08-01.csv` is for arrivals to
  London Heathrow Airport (ICAO's id EGLL) on Aug, 1 2017.
  Key data items:
    * `flight_id`     unique flight identification
    * `callsign`      callsign flight identification of flight
    * `aircraft_reg`  aircraft registration
    * `aircraft_type` aircraft type, ICAO coding (e.g. A388, B772)
    * `adep` / `ades`   aerodrome of departure / destination

@@

The position reports within 40 nautical miles for arrival at
`<airport>` on `<date>`  are in a CSV file 
`<airport>_pos_rt_40NM_<date>.csv`.
These are a subset from `<airport>_pos_rt_<date>.csv`.
For example `eidw_pos_rt_40NM_2017-08-02.csv` is for arrivals'
positions within 40 nautical miles to Dublin Airport
(ICAO's id EIDW) on Aug, 2 2017.
Key data items:

  * `flight_id`     unique flight identification
  * `timestamp`     position report time
  * `latitude`      latitude coordinate (decimal notation)
  * `longitude`     longitude coordinate (decimal notation)
  * `on_ground`     on-ground / aloft flag
  * `distance`      flown distance
  * `distance_arp`  distance position to aerodrome reference point

@@

No files are version controlled in `data-raw`.
